Flat-histogram method comparison on 2D Ising model

### 2020-05-01 ising/ising.tex
wrote a short section describing specific heat capacity plot.
added the conclusion to thesis.
added gas storage to thesis pommerenck.

\title{Flat-histogram method comparison on 2D Ising Model
}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv.pdf}
    \caption{
    The specific heat capacity versus the reciprocal temperature $\beta$ for the $N=32 \times 32$ system for each histogram method.}
    \label{fig:N32-cv}
  \end{figure}

@@

>>>>

\title{Flat-histogram method comparison on 2D Ising model
}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv.pdf}
    \caption{
    The specific heat capacity versus the reciprocal temperature $\beta$ for the $N=32 \times 32$ system for each histogram method at $10^{9}$ moves.}
    \label{fig:N32-cv}
  \end{figure}

@@

Fig.~\ref{fig:N32-cv} shows the specific heat capacity vs. the reciprocal temperature $\beta$ at $10^{9}$ moves. Each method (except for the SAMC methods) is shown using the same single random number seed.
